\mytitle{}

### 2018-02-14 marl-report/report.tex
Report progress/fixes

\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}

@@

\usepackage{booktabs}
\usepackage{microtype}

@@

Yeahh..

\paragraph{Network topology.}
As in the paper. (describe here? TikZ graph?)

?? Simple enough flow rules, just send up the tree indiscriminately. The model doesn't concern the server having to reply to its clients, mysteriously. Oh well.

@@

\paragraph{Pushback.}
Mininet's switches run \emph{Open vSwitch} (OvS), allowing them to be remotely configured via \emph{OpenFlow} messages.
To enable pushback via probabilistic packet dropping as in the original experiment, OvS was modified to include a custom action to do just this for any given flow.

Typically, OvS switches register with a single controller: when a packet which can't be routed arrives, the switch forwards this to the controller, which is responsible for replying with new rules to make delivery possible.
The control application acts outside of the typical Switch--Controller relationship: given that rule updates must be periodically posted \emph{at the control application's discretion}, the flow updates are manually composed and sent directly.

@@

The monitoring daemon spawns one thread for each interface it's told to subscribe to.
Each of these threads then handles the \emph{libpcap} events attached to that interface, determining whether a packet is `good' or `bad' and appending the packet length to a dedicated location in a shared store.
Every timestep, the calling program locks the shared store and reads out the time difference, traffic counts, and classifications for each interface.
These statistics enable a rough calculation of the current load in \si{\mega\bit\per\second}.

\paragraph{Reinforcement learning.} Opportunistic SARSA! ($\gamma = 0$, no discounting)

For an action $a-t$ chosen by the current value function $Q_t$ while in state $s_t$ ??CLEANUP:

$$ Q_{t+1}(s_t,a_t) = Q_t(s_t,a_t) + \alpha [R_{t+1} + \gamma Q_t(s_{t+1},a_{t+1}) - Q_t(s_t,a_t)] $$
Actions received from each learner cause a different level of throttling to be applied within the network.

?? Tabular approximation, tile coding, maybe list the params here?!

\paragraph{Changes for experiments 2... 3...} Undecided.

@@

Yikes!

>>>>

\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{amsmath}

@@

\usepackage{booktabs}
\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,spacing=true]{microtype}

@@

\paragraph{Network topology.}
As in the paper:
\begin{itemize}
	\item The topology contains one server node which has a fixed bandwidth $U_s$ to a dedicated switch.

	\item The task of DDoS defence is divided between $n$ teams.
	Each team's leader switch connects to the server's switch.

	\item Each team then has $m$ intermediate switches, which are connected to it.

	\item Every intermediate router has $k$ connected switches which each host a reinforcement learning agent.
	An `external' router is connected to each learner---this is an adaptation to move from the previous ISP-like notion of a topology to be more extensible.

	\item Each `external' router then admits $\ell$ hosts.
	Each host is \emph{legitimate} or an \emph{attacker} according to some fixed probability, which governs the volume of bandwidth it sends to the server.
\end{itemize}
This model does not require that the server respond or serve its clients, allowing some simplification: the only flow rules forward packets towards the server indiscriminately.

@@

@@

The monitoring daemon spawns one thread for each interface it told to subscribe to.
Each of these threads then handles the \emph{libpcap} events attached to that interface, determining whether every received packet is `good' or `bad' and appending the packet length to a dedicated location in a shared store.
Every timestep, the calling program locks the shared store and reads out the time difference, traffic counts, and classifications for each interface.
These statistics enable a rough calculation of the current load across each interface in \si{\mega\bit\per\second}.

\paragraph{Reinforcement learning.} As in the original experiment, I use opportunistic SARSA to learn the state-action value function.
In this variant, the discount factor is removed ($\gamma = 0$), so the model does not encode or learn any longer term planning (i.e.\ take a worse state to eventually reach a more optimal state).

Action selection and learning are simple.
The agent maintains a \emph{value function} $Q(s, a)$, encoding the \emph{value} of taking any action from a given state.
Here, we consider an $\epsilon$-greedy process: a random action is chosen with probability $\epsilon$, otherwise the action with the highest value in the current state is chosen.
This allows for exploration, and is thus linearly annealed.
If exploration is to stop after $t_{end}$ iterations, we write:
\begin{equation}
\epsilon(t) = \epsilon_0(1 - \max[1, t/t_{end}])
\end{equation}
For an action $a_t$ chosen by the current value function $Q$ while in state $s_t$, we observe a \emph{reward} $R_{t+1}$ at the next timestep along with state $s_{t+1}$.
The model may then be updated:
\begin{align}
\begin{split}
Q(s_t,a_t) \leftarrow Q(s_t,a_t) + \alpha [R_{t+1} + \gamma Q(s_{t+1},a_{t+1}) - Q(s_t,a_t)] \\
= Q(s_t,a_t) + \alpha [R_{t+1} - Q(s_t,a_t)] 
\end{split}
\end{align}
When discounting is zero as above, SARSA and Q-learning become equivalent.
The learned policy is thus unaware of the action-selection strategy.

%?? Tabular approximation, tile coding, maybe list the params here?!
The current state for a learner is initially a vector containing the bandwidths observed along the route from that learner to the server.
This is discretised using \emph{tile coding}.
The reward $R_t$ for any learner is computed from the proportions of `good' traffic received at the server switch and the team leader, with explicit punishment for saturating the core link.

\paragraph{Pushback.}
Actions received from each learner cause a different level of throttling to be applied within the network---dropping \SIrange{0}{90}{\percent} of traffic forwarded from each learning agent's switch.
This functionality is introduced to Mininet by modification of \emph{Open vSwitch} (OVS).

Mininet's switches run OVS, allowing them to be remotely configured via \emph{OpenFlow} messages.
To enable pushback via probabilistic packet dropping as in the original experiment, the kernel module of OVS was modified to include a custom action to do just this for any given flow.
This action takes the form $\operatorname{PDrop(\mathit{prob})}$, for some integer $\mathit{prob} \in [0, 2^{32}-1]$: for some $x$ uniformly drawn from the same domain, if $x < \mathit{prob}$ then the rest of the actions execute as normal.

Typically, OVS switches register with a single controller: when a packet which can't be routed arrives, the switch forwards this to the controller, which is responsible for replying with new rules to make delivery possible.
The control application acts outside of the typical Switch--Controller relationship: given that rule updates must be periodically posted \emph{at the control application's discretion}, the flow updates are manually composed and sent directly.

\paragraph{Changes for experiments 2... 3...}
Undecided.
Experiment 2 concerns (in theory) adding more and more hosts and seing if the performance ceiling is lowered.
(I.e.\ the bound on how much legit traffic you can get to the server decreases)

Issue w/ experiment 3 is that it's hard to get any meaningful variance if we can't have a large ``max-pool'' of hosts.
I suppose you could keep the total the same, but play about with how the hosts distribute such that there isn't an overload if that always leads to failure anyway.

@@

Inconclusive.
